\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{multirow}
\usepackage{float}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Estimate Power generation of invisible solar site using State estimation\\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
\thanks{PEA, AIT, NEU}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Pornchai Chaweewat}
\IEEEauthorblockA{\textit{EECC} \\
\textit{AIT)}\\
Pathumthani, Thailand \\
chaweewat.p@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Weerakorn Ongsakul}
\IEEEauthorblockA{\textit{EECC} \\
\textit{AIT)}\\
Pathumthani, Thailand \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Jai Govind Singh}
\IEEEauthorblockA{\textit{EECC} \\
\textit{AIT)}\\
Pathumthani, Thailand \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Ali abur}
\IEEEauthorblockA{\textit{EEC} \\
\textit{NEU}\\
Boston, MA, USA \\
email address}
}

\maketitle

\begin{abstract}
The number of large scale and rooftop scale solar photovoltaic (PV) systems in electricity grid is growing at exponential rate.
Invisible solar PV refers to small-scale and rooftop solar sites in distribution system that are not mornitored by utilities.
These invisible solar PV sites cause challenging to utilies and system operators.
In this paper, a methodology is proposed to identify location and estimate installation capacity of solar PV sites.
With measurement voltage at any buses and power flow in any lines, state estimation (SE) algorithm could find power consumption in any buses.
The consumption are fed to find correlation with solar irradaiton data.
Thus, the correlative between these data could locate the site of invisible solar PV sites.
Futhermore, the change point method and proposed algorithm could estimate installation capacity of invisible solar PV sites.
The proposed methodology is test in distribution system i.e, four bus system and CIGRE Medium voltage distribution network with PV and Wind DER with randomly invsisble solar PV sites location.
The overall results of the study shows that the correlation between consumption and solar irradiation can perfectly identify invisible solar PV sites with $\text{F}_{1}$ score aboved 0.96 and Matthews correlation coefficient (MCC) score aboved 0.90.
The installation capacity estimation performe good with mean absolute error (MAPE) below 17\%.
\end{abstract}

\begin{IEEEkeywords}
  Solar photovoltaic, invisible solar PV site, Gaussian noise, state estimation, correlation, change point detection, Matthews correlation coefficient
\end{IEEEkeywords}


\input{Introduction}
\input{Literature}
\input{Formulation}
\input{results}
\section{Conclusion}
Here is Conclusion.
\section*{Acknowledgment}

\input{References}





\end{document}
