\begin{thebibliography}{00}
  \bibitem{b18} K. Mathiesen. (Jan. 2016). What is holding back the growth of solar power?. [online]. Available: https://www.theguardian.com/sustainable-business/2016/jan/31/solar-power-what-is-holding-back-growth-clean-energy.
  \bibitem{b19} I. Ost I. (May. 2018). The Price of a Solar Panel System over the Years. [online]. Available: https://blog.pickmysolar.com/the-price-of-a-solar-panel-system-over-the-years.
  \bibitem{b26} P. Fairley. (Jan. 2015). Hawaii’ s Solar Push Strains the Grid. [online]. Available: http://www.technologyreview.com/news/534266/ hawaiis-solar-push-strains-the-grid/
  \bibitem{b15} W. Staff. (Sep. 2014). Heco Customers Asked to Disconnect Unauthorized PV Systems. [Online]. Available: http://khon2.com/2014/ 09/05/heco-customers-asked-to-disconnect-unauthorized-pv-systems/.
  \bibitem{b16} V. Schwarzer and R. Ghorbani, “Transient over-voltage mitiga- tion: Explanation and mitigation options for inverter-based dis- tributed generation projects,” Elect.Vehicle Transp. Center, Sch. Ocean Earth Sci. Technol., Univ. Hawai’ i Manoa, Honolulu, HI, US A , Tech. Rep. HNEI-02-15, Feb. 2014.
  \bibitem{b17} B. Palma. (Sep. 2017). Is It Illegal in Florida to Power Your Home With Solar After a Storm Because of Lobbying?. [online]. Available: https://www.snopes.com/fact-check/is-it-illegal-florida-power-home-solar-storm/.
  \bibitem{b30} B. Sipe. (Jul. 2006). Renewable Energy System Permit Fees in Oregon. [online]. Available: https://www.energytrust.org/wp-content/uploads/2016/11/0609\_SolarPermitFees0.pdf.
  \bibitem{b20} M. E. Baran, H. Hooshyar, Z. Shen, and A. Huang, “Accommodating high PV penetration on distribution feeders,” IEEE Trans. Smart Grid, vol. 3, no. 2, pp. 1039–1046, Jun. 2012.
  \bibitem{b21} M. J. Reno, K. Coogan, R. J. Broderick, J. Seuss, and S. Grijalva, “Impact of PV variability and ramping events on distribution voltage regulation equipment,” in Proc. IEEE Photovolt. Spec. Conf., Tampa, FL, USA, 2014.
  \bibitem{b24} A. Samadi, L. Söder, E. Shayesteh, and R. Eriksson, “Static equivalent of distribution grids with high penetration of PV systems,” IEEE Trans. Smart Grid, vol. 6, no. 4, pp. 1763–1774, Jul. 2015.
  \bibitem{b25} H. Ravindra et al.,“Impact of PV on distribution protection system,” in Proc. North Amer. Power Symp. (NAPS), Champaign, IL, USA, Sep. 2012, pp. 1–6.



  \bibitem{b9} A. Primadianto and C. Lu, "A Review on Distribution System State Estimation," in IEEE Transactions on Power Systems, vol. 32, no. 5, pp. 3875-3883, Sept. 2017.
  \bibitem{b5} Haibin Wang and N. N. Schulz, "A revised branch current-based distribution system state estimation algorithm and meter placement impact," in IEEE Transactions on Power Systems, vol. 19, no. 1, pp. 207-213, Feb. 2004.
  \bibitem{b7} M. Baran and T. E. McDermott, "Distribution system state estimation using AMI data," 2009 IEEE/PES Power Systems Conference and Exposition, Seattle, WA, 2009, pp. 1-3.
  \bibitem{b6} J. Pereira, J. T. Saraiva and V. Miranda, "An integrated load allocation/state estimation approach for distribution networks," 2004 International Conference on Probabilistic Methods Applied to Power Systems, Ames, IA, 2004, pp. 180-185.
  \bibitem{b4} R. Sharifian, E. Jafari, M. Rahimi, P. Ghaebi Panah, "State estimation for load allocation in distribution systems," International Journal on “Technical and Physical Problems of Engineering”, vol. 4, no. 1, pp. 86-90, Mar. 2012.

  \bibitem{b10} Nathan Wallace, Stanislav Ponomarev, and Travis Atkison, "Identification of Compromised Power System State Variables", International Conference on Information and Knowledge Engineering, Nevada, USA, 2014.
  \bibitem{b8} G. Chaojun, P. Jirutitijaroen and M. Motani, "Detecting False Data Injection Attacks in AC State Estimation," in IEEE Transactions on Smart Grid, vol. 6, no. 5, pp. 2476-2483, Sept. 2015.
  \bibitem{b11} X. Zhang and S. Grijalva, “A data-driven approach for detection and estimation of residential pv installations,” IEEE Transactions on Smart Grid, vol. 7, no. 5, pp. 2477–2485, Sept 2016.
  \bibitem{b12} H. Shaker, H. Zareipour, and D. Wood, “Estimating power generation of invisible solar sites using publicly available data,” IEEE Transactions on Smart Grid, vol. 7, no. 5, pp. 2456–2465, Sept 2016.
  \bibitem{b13} H. Jiang, X. Dai, D. W. Gao, J. J. Zhang, Y. Zhang, and E. Muljadi, “Spatial-temporal synchrophasor data characterization and analytics in smart grid fault detec- tion, identification, and impact causal analysis,” IEEE Transactions on Smart Grid, vol. 7, no. 5, pp. 2525– 2536, Sept 2016.
  \bibitem{b14} X. He, R. Qiu, L. Chu, Q. Ai, Z. Ling, J. Zhan, Detection and estimation of the invisible units using utility data based on random matrix theory, Oct. 2017, [online] Available: https://arxiv.org/abs/1710.10745.

  \bibitem{b2} A. Abur and A. G. Exposito, Power System State Estimation: Theory and Implementation. New York: Marcel Dekker, 2004.
  \bibitem{b1} Roytelman I. and S.M. Shahidehpour, ‘State estimation for electric power distribution systems in quasi real-time conditions’, IEEE Trans. Power Systems, 1993 winter meeting, paper no:090-1-PW RD.
  \bibitem{b27} M. A. Hall, “Correlation-based feature subset selection for machine learning,” Ph.D. dissertation, Dept. Comput. Sci., Univ. Waikato, Hamilton, New Zealand, 1999.
  \bibitem{b28} "Comparison of the predicted and observed secondary structure of T4 phage lysozyme"
  \bibitem{b29}  Powers, David M W (2011). "Evaluation: From Precision, Recall and F-Measure to ROC, Informedness, Markedness & Correlation" (PDF). Journal of Machine Learning Technologies. 2 (1): 37–63


  \bibitem{b3} CIGRE' Task Force C6.04.02: Developing benchmark models for integrating distributed energy resourcesS. Barsali, Kai Strunz, Zbigniew StyczynskiPublished 2005

\end{thebibliography}
